A Reimplementation of Python’s dict using Simple Tabulation Hashing and Linear Probing

### 2012-05-20 docs/paper.tex
Capitalization of python

\begin{abstract}
Here we implement simple tabulation hashing with linear probing in Python dictionary based on the recent theoretical result of Patrascu et al. Although we achieved small performance wins on the order of 4\%, we were unable to achieve significant performance wins.  The time and memory required to compute the ST hash are too large to justify the speedup garnered by switching to simple tabulation hashing and linear probing.
\end{abstract}

\section{Introduction}
In this project we aim to analyze and improve the performance of Python's dictionary or dict.  Python is an extremely popular general purpose computing language for several reasons:
\begin{enumerate}
 \item Clean, elegant near-pseudo code syntax leads to clear code 
 \item Widely distributed and available
 \item Large quantity of external libraries for specific features 
\end{enumerate}

@@

Our primary benchmark was a synthetic one that called the CPython dictionary
code directly from C so that all the interpreter overhead was bypassed.  We
measured performance for both sequential strings, generated by converting
sequential integers into their string representation, and for random strings,
generated by the string representation of random integers.  For each of the
benchmarks, we inserted a given number of keys into the dictionary and measured
the runtime.

>>>>

\begin{abstract}
Here we implement simple tabulation hashing with linear probing in Python
dictionary based on the recent theoretical result of Patrascu et al. Although
we achieved significant performance wins on synthetic benchmarks, on real
benchmarks our wins were only on the order of 4\%.  When viewed as a whole, the
extra memory bandwidth
and latency required to compute the simple tabulation hash are too large to
justify the dictionary speedup garnered by switching to simple tabulation hashing and linear probing.
\end{abstract}

\section{Introduction}
In this project we aim to analyze and improve the performance of Python's
dictionary or dict by changing its underlying implementation.  Python is an extremely popular general purpose computing language for several reasons:
\begin{enumerate}
 \item Clean, elegant near-pseudo code syntax leads to clear code 
 \item Widely distributed and available
 \item Large quantity of external libraries for specific features 
\end{enumerate}

@@

Our primary benchmark, hash-table-shootout, is a synthetic one that called the CPython dictionary
code directly from C so that all the interpreter overhead was bypassed.  We
measured performance for both sequential strings, generated by converting
sequential integers into their string representation, and for random strings,
generated by the string representation of random integers.  For each of the
benchmarks, we inserted a given number of keys into the dictionary and measured
the runtime.
